Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-18 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
小修改

\subsubsection{Datasets}
We evaluate our universal perturbations on several tracking datasets: OTB2015 \cite{OTB}, GOT-10k Val \cite{GOT-10k}, and LaSOT \cite{LaSOT}.
The detailed information and evaluation metrics of each dataset are described in the following subsections.

@@

GOT-10k \cite{GOT-10k} is a recent large-scale high-diversity dataset. There is no overlap in object classes between the train/val/test splits, promoting the importance of generalization to unseen object classes.
%Because we need to use the real ground truth to generate the fake ground truth, and the fake ground truth is not available on test set, so we use the val set.
%The evaluation metric is AO and Success rate, which means ...
We use the average overlap (AO) for evaluation.
The AO relative to $B^{fake}$ on the adversarial videos is 0.818, which demonstrates that the generated universal perturbations can mislead the track to follow a specified trajectory (see Figure \ref{fig:vis}).
%On GOT-10k Val set, the AO relative to $B^{gt}$ on the clean videos is 0.760. The AO relative to $B^{gt}$ on the adversarial videos is 0.023.

@@

We implement a series of experiments to analyse and evaluate the contribution of each loss component.
In Table \ref{tab:loss}, we report our results on GOT-10k val set with different combination of loss terms, where $L_{cls}, L_{quality}, L_{reg}$ represent the classification loss, the quality assessment loss and the regression loss in Equ. \ref{eq:loss}, respectively.
To summarize, while all loss terms are beneficial, the classification term is more efficient than the quality assessment term.

@@

As shown in Table \ref{tab:iter}, after approximately 30000 training iterations, the generated perturbations could fool most targets in GOT-10k Val. The AO relative to $B^{gt}$ falls down from 0.760 to 0.035. We notice that at the start of the training period (when training iteration is less than 2048), the falling speed of AO relative to $B^{gt}$ is the largest. This demonstrates the efficiency of our end-to-end training pipeline used to generate the adversarial perturbations.

>>>>

\subsubsection{Datasets}
We evaluate our universal perturbations on several tracking datasets: OTB2015 \cite{OTB}, GOT-10k\_Val \cite{GOT-10k}, and LaSOT \cite{LaSOT}.
The detailed information and evaluation metrics of each dataset are described in the following subsections.

@@

GOT-10k \cite{GOT-10k} is a recent large-scale high-diversity dataset. There is no overlap in object classes between the train/val/test splits, promoting the importance of generalization to unseen object classes.
%Because we need to use the real ground truth to generate the fake ground truth, and the fake ground truth is not available on test set, so we use the val set.
%The evaluation metric is AO and Success rate, which means ...
We use the average overlap (AO) for evaluation.
The AO relative to $B^{fake}$ on the adversarial videos is 0.818, which demonstrates that the generated universal perturbations can mislead the track to follow a specified trajectory (see Figure \ref{fig:vis}).

@@

We implement a series of experiments to analyse and evaluate the contribution of each loss component.
In Table \ref{tab:loss}, we report our results on GOT-10k val set with different combination of loss terms, where $L_{\text{cls}}, L_{\text{quality}}, L_{\text{reg}}$ represent the classification loss, the quality assessment loss and the regression loss in Equ. \ref{eq:loss}, respectively.
To summarize, while all loss terms are beneficial, the classification term is more efficient than the quality assessment term.

@@

As shown in Table \ref{tab:iter}, after approximately 30000 training iterations, the generated perturbations could fool most targets in GOT-10k\_Val. The AO relative to $B^{gt}$ falls down from 0.760 to 0.035. We notice that at the start of the training period (when training iteration is less than 2048), the falling speed of AO relative to $B^{gt}$ is the largest. This demonstrates the efficiency of our end-to-end training pipeline used to generate the adversarial perturbations.
